CONEM2024-0025\\ NEW ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-03-12 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating data - small corrections

	One of the approaches that widely applied to clustering products according to their importance is the multicriteria ABC classification. The scientific literature broadly emphasizes the value of multicriteria ABC classification for inventory management and presents several multicriteria methods. The Analytical Hierarchy Process is one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}. Some recent studies also emphasize the importance of applying multicriteria analysis to strategic planning \citep[\emph{e.g.},][]{BarbosaDePaula2022, Pereira2023, MarianoRibeiro2023}. \citet{Odu2019} emphasizes that, when applying some multicriteria methods, it is crucial to pay particular attention to the objectivity factors of criteria weights. The author provides a detailed overview of different weighting methods applicable to multicriteria techniques.

@@

The bottomLeftCorner() function is similar to the topLeftCorner() function. In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the third row ($M[m_{\{sz\}j}]_{sz=3}$), and then the elements of the next rows are evaluated, following the order from top to bottom. In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-3$), then the elements of the previous rows are evaluated, following the order from bottom to top.

@@

As discussed earlier, in our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification.

@@

	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of Willians. A single measure was adopted for these two criteria (lead time billing  weight) dividing the billing by the complement of the lead time for each product and then normalizing the weights.

In the case of qualitative criteria, the initial ABC classification was made using three weights, one weight assigned to products A, pa, a second weight assigned to products B, pb, and a third weight assigned to products C, pc, where pa > pb > pc. For qualitative criteria, pa, pb and pc must be assigned using the following steps:

\begin{itemize}
\item order the products, in descending order, according to their respective values for lead time billing;
\item classify products into three groups, A, B and C, for each qualitative criterion;
\item do pc = 0 for all group C products, for each qualitative criterion;
\item for each qualitative criterion, do peer-to-peer comparison with the groups A and B and the products ordered according to the lead time billing criterion, answering the following question: the degree of importance of the products of this group to the qualitative criterion is equivalent to what degree of importance of the other product evaluated according to the lead time billing criterion ?;
\item assign to pa and pb the value of the lead time billing of the product with corresponding importance.
\end{itemize}

Equations (\ref{eq:leadTimeBillingWeight}) and (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:

@@

$w_{pc}$ is the weight percentage of the product $p$ according to criterion $c$;

@@

As we can see in this table, the pairwise comparison weights are adjusted primarily according to the weights assigned to the first three criteria. Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria are preserved. The algorithm will change the weights of the other criteria to force the consistency of the pairwise comparisons matrix. Another significant observation is that the algorithm stops when it reaches the desired consistency rate. So, it is more likely that the algorithm changes the weights related to the fourth criterion and the next ones. Therefore, in the preparation of the input file the data of the criteria must be informed in such a way that the criteria are ordered in descending order according to their respective relevance.

@@

a Tab. \ref{tab:pairwiseMatrixAdjusted} apresenta uma comparação dos resultados usando diferentes métodos. Na matrix PCM 02, o método para forçar consistência foi aplicado antes da reordenação dos critérios antes. Já no caso da matrix PCM 03, o método para forçar consistência foi aplicado após a reordenação dos critérios. Esta tabela também mostra a matrix PCM 04 com os ajustes realizados pelo dono da empresa na matrix PCM 01 após verificar os resultados encontrados pelo COPSolver. Conforme podemos verificar, o software COPSolver provê uma importante ajuda na elaboração de tabelas de comparação por pares consistentes. Verificamos também que é importante realizar a ordenação dos critérios antes de ajustar a matriz buscando uma melhor consistência, pois os pesos atribuídos para os critérios mais relevantes devem ser preferencialmente mantidos. Finalmente, observamos que a ordenação dos critérios também ajuda no ajuste manual das matrizes de comparação por pares, já que a apresentação destas tabelas com os critérios ordenados facilita a análise dos pesos.  Para classificação multicritério dos itens foi utilizada a matriz de comparação por pares PCM 04, tendo em vista a importância da avaliação final realizada pelo funcionário responsável ou dono da empresa.

\begin{table}[ht]
            \begin{center}
                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; bl = billing; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
                    \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
                        \\
   						\multicolumn{14}{c}{furniture trades company} \\
   						\cline {1-15} \\
   						\multicolumn{7}{l}{PCM 01 - original data reordered} & & \multicolumn{7}{l}{PCM 02 - PCM 01 adjusted and than reordered} \\
						\cline {1-15} \\
  						& \multicolumn{7}{c | }{CR = 0.136}  & \multicolumn{7}{c}{CR = 0.096} \\
  						& \multicolumn{7}{c | }{$w=(0.48, 0.26, 0.13, 0.07, 0.03, 0.03)$}  & \multicolumn{7}{c}{$w = (0.35, 0.35, 0.16, 0.09, 0.03, 0.03)$} \\
   						& bl & cr & rp & lt & ob & cm & & bl & cr & rp & lt & ob & cm \\        
						bl & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 & & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 7.00 & 9.00 & 9.00 \\
						cr & 0.33 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 \\
						rp & 0.14 & 0.33 & 1.00 & 5.00 & 3.00 & 5.00 & & \cellcolor[HTML]{ACE600} 0.33 & 0.33 & 1.00 & 5.00 & 3.00 & 5.00 \\
						lt & 0.11 & 0.14 & 0.20 & 1.00 & 5.00 & 7.00 & & \cellcolor[HTML]{ACE600} 0.14 & 0.14 & 0.20 & 1.00 & 5.00 & 7.00 \\
						ob & 0.11 & 0.11 & 0.33 & 0.20 & 1.00 & 1.00 & & 0.11 & 0.11 & 0.33 & 0.20 & 1.00 & 1.00 \\
						sb & 0.11 & 0.11 & 0.20 & 0.14 & 1.00 & 1.00 & & 0.11 & 0.11 & 0.20 & 0.14 & 1.00 & 1.00 \\
						\cline {1-15} \\
						\multicolumn{7}{l}{PCM 03 - PCM 01 reordered and than adjusted} & & \multicolumn{7}{l}{PCM 01 - manually adjusted based on COPSolver results} \\
						\cline {1-15} \\
  						& \multicolumn{7}{c | }{CR = 0.082}  & \multicolumn{7}{c}{CR = 0.082} \\
  						& \multicolumn{7}{c | }{$w=(0.49, 0.27, 0.11, 0.06, 0.05, 0.03)$}  & \multicolumn{7}{c}{$w = (0.50, 0.25, 0.12, 0.08, 0.03, 0.03)$} \\
   						& bl & cr & rp & lt & ob & cm & & bl & cr & rp & lt & ob & cm \\        
						bl & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 & & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 \\
						cr & 0.33 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 9.00 & 9.00 \\
						rp & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & 3.00 & 5.00 & & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 5.00 \\
						lt & 0.11 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 7.00 & & 0.11 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & 5.00 & \cellcolor[HTML]{ACE600} 5.00 \\
						ob & 0.11 & 0.11 & 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & & 0.11 & 0.11 & \cellcolor[HTML]{ACE600}  0.20 & 0.20 & 1.00 & 1.00 \\
						sb & 0.11 & 0.11 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & & 0.11 & 0.11 & 0.20 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & 1.00 \\
						\cline {1-15} \\
				\end{tabular} \label{tab:pairwiseMatrixAdjusted}
            \end{center}
	\end{table}

\subsection{Analysis on the New ABC Multicriteria Classification Method}

\begin{table}[h!]
\begin{center}
\begin{small}
\begin{tabular}[c]{l r r | l r r r r}
\multicolumn{8}{l}{car mechanics company} \\
\cline {1-8} \\
\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
\multicolumn{3}{c |}{cutoff}  & \multicolumn{5}{c}{75 sales between October 2020 and July 2023} \\
\multicolumn{3}{c |}{0.35 \%; 0.70 \%} & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
A &  10 & 23.81 \% & smooth & 18.75 \% &  20.00 \% & 16.67 \% & 0 \%\\
B &  15 & 35.71 \% & slow-moving & 6.25 \% & 10.00 \% & 0.00 \% & 0 \%\\
C &  17 & 40.48 \% & sporadic & 75.00 \% & 70.00 \% & 83.33 \% & 0 \% \\
\cline {1-8} \\
\multicolumn{8}{l}{furniture trades company} \\
\cline {1-8} \\
\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
\multicolumn{3}{c |}{cutoff:} &\\
\multicolumn{3}{c |}{0.35 \%; 0.70 \%}& & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
A &  26 & 10.24 \% & smooth & 31.58 \% &  73.08 \% & 30.00 \% & 24.82 \%\\
B &  80 & 31.50 \% & slow-moving & 18.62 \% & 19.23 \% & 33.75 \% & 9.93 \%\\
C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 36.25 \% & 65.25 \% \\
\cline {1-8} \\
 \multicolumn{8}{l}{plastic packaging manufacturing company}\\
\cline {1-8} \\
\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
\multicolumn{3}{c |}{cutoff:} & \multicolumn{5}{c}{5,967 sales between November 2019 and February 2023}\\
\multicolumn{3}{c |}{0.35 \%; 0.70 \%} & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
A &   128 &  5.49 \% & smooth & 15.31 \% & 22.66 \% & 23.97 \% & 10.42 \%\\
B &   726 & 31.12 \% & slow-moving & 5.53 \% & 1.56 \% & 8.68 \% & 4.33 \%\\
C & 1,479 & 63.39 \% & sporadic & 79.16 \% & 75.78 \% & 67.36 \% & 85.25 \% \\
\cline {1-8} \\

\end{tabular}
\caption{ABC multicriteria and demand pattern classifications for three companies (results found by COPSolver)}
\label{tab:results}
\end{small}
\end{center}
\end{table}

@@

        \section{CRediT authorship contribution statement} 
		\label{sec:contributions}

@@

        Os trabalhos escritos em português ou espanhol devem incluir (após direitos autorais) título, os nomes dos autores e afiliações, o resumo e as palavras-chave, traduzidos para o inglês e a declaração a seguir, devidamente adaptada para o número de autores.

        O(s) autor(es) é(são) o(s) único(s) responsável(is) pelo conteúdo deste trabalho.

>>>>

	One of the approaches that is widely applied to clustering products according to their importance is the multicriteria ABC classification. The scientific literature broadly emphasizes the value of multicriteria ABC classification for inventory management and presents several multicriteria methods. The Analytical Hierarchy Process is one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}. Some recent studies also emphasize the importance of applying multicriteria analysis to strategic planning \citep[\emph{e.g.},][]{BarbosaDePaula2022, Pereira2023, MarianoRibeiro2023}. \citet{Odu2019} emphasizes that, when applying some multicriteria methods, it is crucial to pay particular attention to the objectivity factors of criteria weights. The author provides a detailed overview of different weighting methods applicable to multicriteria techniques.

@@

The bottomLeftCorner() function is similar to the topLeftCorner() function. In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the third row ($M[m_{\{sz\}j}]_{sz=3}$), and then the elements of the next rows are evaluated, following the order from top to bottom. In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-2$), then the elements of the previous rows are evaluated, following the order from bottom to top.

@@

As discussed earlier, in our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification, that is, assign weights to each product according to each criterion.

@@

The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of \cite{Williams1984}. A single measure was adopted for these two criteria (lead time billing  weight) dividing the billing by the complement of the lead time for each product and then normalizing the weights.

In the case of qualitative criteria, the initial ABC classification was made using three weights, one weight assigned to group A products, $w(A)$, a second weight assigned to group B products, $w(B)$, and a third weight assigned to products C, $w(C)$, where $w(A) > w(B) > w(C)$. For qualitative criteria, $w(A)$, $w(B)$ and $w(C)$ must be assigned using the following steps:

\begin{itemize}
\item order the products, in descending order, according to their respective values for lead time billing;
\item classify products into three groups, A, B and C, for each qualitative criterion;
\item do $w(C)$ = 0 for all group C products, for each qualitative criterion;
\item for each qualitative criterion, do peer-to-peer comparison with the groups A and B products and the products ordered according to the lead time billing criterion, answering the following question: the degree of importance of the products of this group to the qualitative criterion is equivalent to what degree of importance of the other product evaluated according to the lead time billing criterion ?;
\item assign to $w(A)$ and $w(B)$ the value of the lead time billing of the product with corresponding importance; 
\end{itemize}

After the correct assignment of the weights for each product according to each criterion, Eqs. (\ref{eq:leadTimeBillingWeight}) and (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:

@@

$w_{pc}$ is the normalized weight percentage of the product $p$ according to criterion $c$;

@@

As we can see in Tab. \ref{tab:pairwiseMatrix}, the pairwise comparison weights are adjusted primarily according to the weights assigned to the first three criteria. Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria are preserved. The algorithm will change the weights of the other criteria to force the consistency of the pairwise comparisons matrix. Another significant observation is that the algorithm stops when it reaches the desired consistency rate. So, it is more likely that the algorithm changes the weights related to the fourth criterion and the next ones. Therefore, in the preparation of the input file the data of the criteria must be informed in such a way that the criteria are ordered in descending order according to their respective relevance.

@@

Table 3 presents a comparison of the results using different methods on the data provided by the furniture trading company. In matrix PCM 02, the method used to force consistency was applied before the reordering of the criteria. In the case of matrix PCM 03, the same method was applied after reordering the criteria. This table also shows the matrix PCM 04 with adjustments made manually to the matrix PCM 01 after verifying the results found by COPSolver. As we can see, the COPSolver software provides an important help in the preparation of consistent pairwise comparison matrices. We also found that it is important to perform the ordering of the criteria before adjusting the matrix seeking better consistency, since the weights assigned to the most relevant criteria should preferably be maintained. It is possible to verify in these tables that the reordering before the application of the method to force consistency causes the changes to be more distributed and are carried out in the weights relative to the least important criteria. Finally, we observe that the ordering of the criteria also helps in the manual adjustment of the pairwise comparison matrices, since the presentation of these tables with the ordered criteria facilitates the analysis of the weights.  For multicriteria classification of items, the pairwise comparison matrix PCM 03 was used. However, in practical cases it is important to have a final assessment of the responsible employee and the matrix used for ABC classification can be a final matrix manually updated by the employee based on the results found by COPSolver.

\begin{table}[ht]
            \begin{center}
                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; bl = billing; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
                    \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.1cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
                        \\
   						\multicolumn{14}{c}{furniture trades company} \\
   						\cline {1-14} \\
   						& \multicolumn{6}{l}{PCM 01 - original data reordered} & & \multicolumn{6}{l}{PCM 02 - PCM 01 adjusted and than reordered} \\
						\cline {1-14} \\
  						& \multicolumn{6}{c}{CR = 0.136}  & & \multicolumn{6}{c}{CR = 0.096} \\
  						& \multicolumn{6}{c}{$w=(0.48, 0.26, 0.13, 0.07, 0.03, 0.03)$} & & \multicolumn{6}{c}{$w = (0.35, 0.35, 0.16, 0.09, 0.03, 0.03)$} \\
   						& bl & cr & rp & lt & ob & cm & & bl & cr & rp & lt & ob & cm \\        
						bl & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 & & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 7.00 & 9.00 & 9.00 \\
						cr & 0.33 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 \\
						rp & 0.14 & 0.33 & 1.00 & 5.00 & 3.00 & 5.00 & & \cellcolor[HTML]{ACE600} 0.33 & 0.33 & 1.00 & 5.00 & 3.00 & 5.00 \\
						lt & 0.11 & 0.14 & 0.20 & 1.00 & 5.00 & 7.00 & & \cellcolor[HTML]{ACE600} 0.14 & 0.14 & 0.20 & 1.00 & 5.00 & 7.00 \\
						ob & 0.11 & 0.11 & 0.33 & 0.20 & 1.00 & 1.00 & & 0.11 & 0.11 & 0.33 & 0.20 & 1.00 & 1.00 \\
						sb & 0.11 & 0.11 & 0.20 & 0.14 & 1.00 & 1.00 & & 0.11 & 0.11 & 0.20 & 0.14 & 1.00 & 1.00 \\
						\cline {1-14} \\
						& \multicolumn{6}{l}{PCM 03 - PCM 01 reordered and than adjusted} & & \multicolumn{6}{l}{PCM 01 - manually adjusted based on COPSolver results} \\
						\cline {1-14} \\
  						& \multicolumn{6}{c}{CR = 0.082}  & & \multicolumn{6}{c}{CR = 0.082} \\
  						& \multicolumn{6}{c}{$w=(0.49, 0.27, 0.11, 0.06, 0.05, 0.03)$} & & \multicolumn{6}{c}{$w = (0.50, 0.25, 0.12, 0.08, 0.03, 0.03)$} \\
   						& bl & cr & rp & lt & ob & cm & & bl & cr & rp & lt & ob & cm \\        
						bl & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 & & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 \\
						cr & 0.33 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 9.00 & 9.00 \\
						rp & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & 3.00 & 5.00 & & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 5.00 \\
						lt & 0.11 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 7.00 & & 0.11 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & 5.00 & \cellcolor[HTML]{ACE600} 5.00 \\
						ob & 0.11 & 0.11 & 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & & 0.11 & 0.11 & \cellcolor[HTML]{ACE600}  0.20 & 0.20 & 1.00 & 1.00 \\
						sb & 0.11 & 0.11 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & & 0.11 & 0.11 & 0.20 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & 1.00 \\
						\cline {1-14} \\
				\end{tabular} \label{tab:pairwiseMatrixAdjusted}
            \end{center}
	\end{table}

\subsection{Analysis On The New ABC Multicriteria Classification Method}

\begin{table}[h!]
\begin{center}
\begin{tabular}[c]{c r r r}
\multicolumn{4}{c}{new ABC Multcriteria Classification with AHP} \\
\\
\multicolumn{4}{l}{car mechanics company} \\
\cline {1-4} \\
\multicolumn{4}{c}{75 sales between October 2020 and July 2023} \\
\\
  &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\
A &  10 & 23.81 \% &  80 \% \\
B &  15 & 35.71 \% &  95 \% \\
C &  17 & 40.48 \% & 100 \% \\
\cline {1-4} \\
\multicolumn{4}{l}{furniture trades company} \\
\cline {1-4} \\
\multicolumn{4}{c}{254 sales between } \\
\\
 &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\

A &  59 & 23.23 \% &  79.78 \%  \\
B &  56 & 22.05 \% &  94.81 \% \\
C & 139 & 54.72 \% & 100.00 \% \\
\cline {1-4} \\

 \multicolumn{4}{l}{plastic packaging manufacturing company}\\
\cline {1-4} \\
\multicolumn{4}{c}{5,967 sales between November 2019 and February 2023} \\
\\
 &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\

A &   128 &  5.49 \% & \\
B &   726 & 31.12 \% & \\
C & 1,479 & 63.39 \% & \\
\cline {1-4} \\

\end{tabular}
\caption{ABC multicriteria classifications for three companies (results found by COPSolver)}
\label{tab:results}
\end{center}
\end{table}

@@

        \section{CRediT AUTHORSHIP CONTRIBUTION STATEMENT} 
		\label{sec:contributions}

@@

        Os autores são os únicos responsávelis pelo conteúdo deste trabalho.
